\section{Results}

A total of 26 studies, concerned with seizure detection, were included in this review (Table number). These studies utilized a range of commercial and non-commercial devices for seizure detection. The most frequently used commercial device was the EMPATICA E4, which was tested in 5 studies \cite{Yu2023-ss, Regalia2019-ch,Nasseri2021-xn, Tang2021-td}. Additional studies employed either customized laboratory-developed devices or other commercial devices, such as: Shimmer \cite{Van_Andel2017-yx, Gheryani2017-yg}, Samsung SM-R800 watch \cite{Vakilna2024-hk}, Mi- Microsoft wristband\cite{Jiang2022-zu}, Nightwatch \cite{Arends2018-ew}, and Biovital P1 System \cite{Wu2024-yl, Wang2025-ql}.

All included studies assessed various combinations of the following physiological and movement sensors and measures: Accelerometer (ACC), Blood Volume Pulse (BVP), Gyroscope (Gyro), Electromyography (EMG), Heart rate (HR), Oxygen Saturation (SPO2), Electrodermal activity (EDA), electrocardiography (ECG), temperature, and Heart rate variability (HRV).

For seizure prediction and forecasting, three studies were found eligible for this review (table number. All three papers used the Empatica E4 wristband device for wearable data acquisition, which includes sensors for electrodermal activity (EDA), blood volume pulse (BVP) via photoplethysmography, 3-axis accelerometry (ACC), and skin temperature; however, the selected modalities for training and analysis differed among the papers.

The number of patients included in data acquisition ranged from 42 \cite{Vieluf2023-ta} to 139 \cite{Vieluf2023-zv} with a mean age ranging from 9.8 \cite{Meisel2020-ii} to 14 \cite{Vieluf2023-ta} years old, indicating a pediatric-dominant cohort. Two studies \cite{Vieluf2023-ta, Vieluf2023-zv} included a control group (patients with no seizures) besides the seizure group to differentiate seizure-related patterns from normal brain activity. All studies were conducted in an in-hospital setting.

\input{Results/demographics}

\input{Results/modalities}

\input{Results/preprocessing}

\input{Results/algorithms}